\documentclass{resume}

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Ahmed Ben Yahia}
\address{+216 50 193 344 \\ Sfax, Tunisia — Open to Remote \& Relocation}
\address{\href{mailto:ahmedbenyahia654@gmail.com}{ahmedbenyahia654@gmail.com} \\ \href{https://linkedin.com/in/ahmedbenyahia}{linkedin.com/in/ahmedbenyahia} \\ \href{https://github.com/levicap}{github.com/levicap} \\ \href{https://ahmedbenyahia-pro-ten.vercel.app/}{ahmedbenyahia-pro-ten.vercel.app}}

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Full Stack Developer with 2+ years of hands-on experience building production SaaS platforms, REST APIs, and e-commerce applications for international clients. Proficient in React, Next.js, Node.js, TypeScript, PostgreSQL, and cloud-native deployment — with a track record of shipping scalable systems on time. Strong background in agile delivery, third-party API integration, and performance-optimized backend architecture. Seeking full-time full stack or backend engineering roles.}

\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages        & TypeScript, JavaScript, Python, Java \\
Frontend         & React, Next.js 14, Tailwind CSS, Recharts, Responsive Design, SSR/SSG \\
Backend          & Node.js, Express.js, NestJS, Spring Boot, REST API, GraphQL, JWT, OAuth2 \\
Databases        & PostgreSQL, MongoDB, Supabase, MySQL, Prisma ORM, Redis \\
DevOps \& Cloud  & Docker, GitHub Actions, Vercel, CI/CD Pipelines, Linux \\
Testing          & Unit Testing, Integration Testing, Postman, Lighthouse \\
Integrations     & Stripe, LinkedIn API, Webflow CMS, OpenAI API, Agora, Twilio, Web3.js \\
Soft Skills      & Agile/Scrum, Technical Scoping, Remote Collaboration, Client Communication \\
\end{tabular}\\

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}

\textbf{AI Automation Engineer} \hfill Nov 2025 -- Present \\
Lean Orchester \hfill \textit{Remote}
\begin{itemize}
    \itemsep -3pt {}
    \item Delivered 15+ production systems for international clients across SaaS, e-commerce, and B2B verticals — maintaining 100\% on-time delivery across all engagements.
    \item Architected and shipped full-stack automation dashboards and reporting pipelines (e.g.\ ServiceM8 KPI pipeline) saving clients 15+ hours/week of manual work.
    \item Built and integrated multi-tenant SaaS features including role-based access control, Stripe billing, and admin reporting dashboards into existing Next.js/Node.js stacks.
    \item Integrated 20+ third-party APIs (Stripe, OpenAI, Twilio, Apollo, Webflow CMS) into production systems with proper error handling and documentation.
\end{itemize}

\textbf{Full Stack Developer Intern} \hfill Jul 2024 -- Aug 2024 \\
Grow Up Agency \hfill \textit{Remote}
\begin{itemize}
    \itemsep -3pt {}
    \item Developed CRUD functionalities and secure authentication for a healthcare management system, improving operational efficiency by 30\%.
    \item Implemented automated email/SMS notification workflows using Node.js, SMTP, and Twilio with real-time dashboards built in Recharts.
\end{itemize}

\textbf{Full Stack Developer Intern} \hfill Feb 2024 -- May 2024 \\
Aziin Engineering Solutions \hfill \textit{Hybrid — Sfax, Tunisia}
\begin{itemize}
    \itemsep -3pt {}
    \item Architected an e-learning SaaS platform from scratch serving 1,000+ concurrent users — featuring live video via Agora SDK, real-time chat, and AI-adaptive learning, boosting user engagement by 35\%.
    \item Implemented JWT/OAuth2 authentication with role-based access control (RBAC), ensuring SOC-2 compliance and integrating Stripe to process \$50K+ in monthly transactions.
    \item Built AI exam generator using GPT-4 with automated grading, cutting instructor workload by 40\% across 500+ students.
    \item Optimized performance with Redis caching and code splitting, achieving 40\% faster load times and a Lighthouse score of 95+.
\end{itemize}

\textbf{Frontend Developer Intern} \hfill Jul 2023 -- Aug 2023 \\
Novel-Ti \hfill \textit{Sfax, Tunisia}
\begin{itemize}
    \itemsep -3pt {}
    \item Designed and optimized the responsive UI for an NFC-based product traceability system, reducing page load time by 20\%.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}

\item \textbf{APIspark — Drag-and-Drop API Builder SaaS.} {Visual platform enabling developers to design production APIs by connecting components, with AI-assisted code generation and automatic OpenAPI documentation. Reduced API scaffolding time from hours to under 15 minutes. Stack: Next.js, Node.js, Prisma, PostgreSQL, OpenAI API. \href{https://apisparkdev.vercel.app/}{(Live)}}

\item \textbf{Postily — AI Social Media Management SaaS.} {Multi-platform SaaS for AI-generated captions and images, content scheduling, queue management, and engagement analytics. Reduced content creation time by 70\%. Stack: Next.js, MongoDB, OpenAI API.}

\item \textbf{Outreach Genie — LinkedIn Outbound SaaS.} {Multi-seat outreach workspace with prospect list management, AI-assisted message generation, campaign sequencing, and full pipeline visibility. Stack: Next.js, PostgreSQL, LinkedIn API, OpenAI API.}

\item \textbf{OlalaHomes — Property Management Dashboard.} {Full-featured internal dashboard tracking occupancy rates, rental revenue, tenant records, and maintenance requests with interactive Recharts visualizations. Saved 15+ hours/week of manual reporting. Stack: Next.js, PostgreSQL, TypeScript.}

\item \textbf{Scenewear — Full E-Commerce Platform.} {End-to-end online store with product catalog, shopping cart, secure checkout, order management, and admin panel — replacing a manual Instagram DM process. Went live in 3 weeks. Stack: Next.js, Spring Boot, PostgreSQL.}

\item \textbf{Ghanem Labs — Web3 Audit SaaS.} {Smart contract security intelligence platform delivering audits, tokenomics analysis, and on-chain threat detection. Stack: Next.js, Node.js, Web3.js, OpenAI API, TypeScript.}

\item \textbf{AI Career Path Mapper.} {Platform that analyzes current role vs. target career goal and generates a personalized 90-day skill-gap roadmap with curated learning resources — in under 30 seconds. Stack: Next.js, Express.js, Gemini API, TypeScript. \href{https://ai-path-carrer-generator.vercel.app/}{(Live)}}

\end{rSection}

%----------------------------------------------------------------------------------------
%	OPEN SOURCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Open Source \& Portfolio}
\begin{itemize}
    \item Built a VS Code-themed interactive developer portfolio with a file explorer, syntax-highlighted project views, and terminal simulation — generating direct hire inquiries from technical reviewers. \href{https://portfolio-eight-gold-99.vercel.app/}{(Live)}
    \item Maintain 35+ public GitHub repositories consistently structured with READMEs, env documentation, and reproducible setups. \href{https://github.com/levicap}{(github.com/levicap)}
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Computer Science} \hfill {2021 -- 2024} \\
Relevant Coursework: Data Structures \& Algorithms, Databases, Software Engineering, Web Development, Object-Oriented Programming, Computer Networks.

\end{rSection}

\end{document}
